SKIN LESION CLASSIFICATION ON IMBALANCED DATA USING DEEP LEARNING WITH SOFT ATTENTION

### 2022-09-12 MDPI/sensors-1915564/template.tex
Update Paper Review 1.1
Update Paper Review 1.3

{Skin lesion classification is not a new area, since there are many great performance models constructed, recent years. The skin classification approaches can be divided into two main approaches: Deep Learning and Machine Learning. Both approaches gain great performance. Data Augmentation and Feature Extractor, otherwise are two main supporters that make the model better.
	\begin{table}[H]
		\centering
		\begin{tabular}{| c | p{1.5cm} | p{1.5cm} | p{2cm} | p{1.5cm} | p{2cm} |}
			\hline
			Research & Deep Learning & Machine Learning & Data 
			Augmentation & Feture Extraction & Data set\\
			\hline
			\cite{03358} & x & & x & & HAM10000\\
			\hline
			\cite{03798} & x & x & x & x & HAM10000\\
			\hline
			\cite{10348} & x & x & x & & HAM10000, $PH^2$\\
			\hline
			\cite{09418} & x & & x & & HAM10000\\
			\hline
			\cite{01284} & x & & x & & HAM10000\\
			\hline
			\cite{06612} & x & & x & x & HAM10000, BCN-20000, MSK\\
			\hline
			\cite{03225} & x & & x & & HAM10000\\
			\hline
			\cite{12602} & x & & x & & HAM10000\\
			\hline
			\cite{03426} & x & & x & & HAM10000\\
			\hline
			\cite{03910} & x & & x & & HAM10000\\
			\hline
			\cite{05045} & & x & x & x & HAM10000\\
			\hline
		\end{tabular}
		\caption{Related Works Summary.}
		\label{table:related-work-summary}
	\end{table}
\subsubsection{Deep Learning Approach}
In Deep Learning, one of the most cutting-edge technologies that have been used is Soft-Attention as stated in \mbox{\cite{03358}}. Soumyyak et al construct several models formed by the combination of a backbone model including DenseNet201 \mbox{\cite{06993}}, InceptionResNetV2 \mbox{\cite{00567}}, ResNet50 \mbox{\cite{03385} \cite{05027}}, VGG16 \mbox{\cite{1556}} and Soft-Attention layer. Their approach is to add the Soft-Attention layer at the end or the middle of the backbone model. For ResNet50 and VGG16, the Soft-Attention layer is added after the third residual block and CNN block, respectively. DenseNet201 and InceptionResNetV2, otherwise concatenate with the Soft-Attention before a fully-connected layer, and then soft-max layer. Soumyyak et al proposed method gain a greate performance and also outperform many other studies with the accuracy of 0.93 and the precision of 0.92. However using the Data Augmentation on an imbalanced data set make the model cannot classify well on all of the classes, therefore their model got the recall and f1-score of 0.71 and 0.75, respectively. In this research, our proposed method also consider this problem and solve it.

Using those above backbones has been tried by many previous papers. Rishu Garg et al \mbox{\cite{03798}} uses transfer learning approach with CNN based model: ResNet50 and VGG16 which are pretrained with ImageNet data set. Besides, they also use data augmentation to avoid the imbalance of the data set. Histogram Equalization is also used to increase the contrast of the skin lesions before feeding into the Machine Learning algorithms including Random Forest, XGBoost, Support Vector Machine.	Histogram Equalization can be consider as a heat map that takes the main feature as the number of occurrences of the same value pixel. This approach also gain great performance with the accuracy of 0.90 and the precision of 0.88. However this approach can be bias since the one skin image of the data set contain the skin lesion at the center and the background skin so that histogram may treat background with more number of occurrence of the same pixel value. In this research, our proposed method use the Soft-Attention which can create a heat map feature of the lesion. Otherwise, Rishu Garg et al proposed method also face the problem of imbalanced classifying due to the imbalanced data set with the f1-score and recall is 0.77 and 0.74, respectively.

@@

@@

@@

\begin{table}[H]
	\centering
	\begin{tabular}{| l | c  c | }
		\hline
		Model & AUC(AD) & AUC(MD)\\ 
		\hline
		InceptionResNetV2 & 0.971 & \textbf{0.975}\\
		\hline
		DenseNet201 & 0.93 & \textbf{0.97}\\
		\hline
		ResNet50 & \textbf{0.95} & 0.93 \\
		\hline
		ResNet152 & 0.97 & 0.87\\
		\hline
		NasNetLarge & - & \textbf{0.96}\\
		\hline
		MobileNetV2 & 0.95 & \textbf{0.97}\\
		\hline
		MobileNetV3Small & - & \textbf{0.96}\\
		\hline
		MobileNetV3Large & 0.96 & \textbf{0.97}\\
		\hline
		NasNetMobile & 0.96 & \textbf{0.97}\\
		\hline
	\end{tabular}
	\caption{AUC (area under the curve) of all models. AD stands for augmented data, this indicate that the model is trained with augmented data. MD stands for Metadata which indicate that the model is trained with Metadata}
	\label{table:overall-auc}
\end{table}

@@

\section{Conclusions}
In this research, our proposed is to construct a model as a combination of backbone models and Soft-Attention. Moreover, the model takes two inputs including image data and metadata. besides, a new weight loss function is applied to figure out the data imbalance problem. Finally, the combination of InceptionResNetV2, Soft-Attention, and Metadata is the best model. Although the accuracy and the precision of the model are not the highest, the f1-score, recall, and AUC-score is the highest and the most balanced indicator. Therefore, InceptionResnetV2 can classify well in all classes including low samples classes. Otherwise, during the experiment, the combination of MobileNetV3, Soft-Attention, and Metadata achieve an accuracy that is nearly the same as InceptionResNetV2, though with fewer number parameters and depth. Therefore the infer time is much less than the InceptionResNetV2. This result opens the door to constructing a great performance model that can be applied to mobile, IoT devices. \add[H.K.D]{As the result, proposed method and others still face the problem of badly distinguish between melanoma and black nevus because in some cases, the melanoma and the nevus image has the same lesion size and color.}
\vspace{6pt}

@@

\dataavailability{The code and the data analysis report can be found here: \\https://github.com/KhoiDOO/Skin-Disease-Detection-HAM100000.git}

@@

\end{thebibliography}

>>>>

{Skin lesion classification is not a new area, since there are many great performance models constructed, recent years. The skin classification approaches can be divided into two main approaches: Deep Learning and Machine Learning. Both approaches gain great performance. Data Augmentation and Feature Extractor, otherwise are two main supporters that make the model better.
\begin{table}[H]
	\centering
	\begin{tabular}{| c | p{1.5cm} | p{1.5cm} | p{2cm} | p{1.5cm} | p{2cm} | p{1cm} |}
		\hline
		Work & Deep Learning & Machine Learning & Data 
		Augmentation & Feature Extractor & Data set & Result\\
		\hline
		\cite{03358} & Classify & & x & & HAM10000 & 0.93 (ACC)\\
		\hline
		\cite{03798} & Classify & Classify & x & x & HAM10000 & 0.9 (ACC)\\
		\hline
		\cite{10348} & Classify & Classify & x & & HAM10000, $PH^2$ & \\
		\hline
		\cite{09418} & Classify & & x & & HAM10000 & 0.88 (ACC)\\
		\hline
		\cite{01284} & Classify & & x & & HAM10000 & 0.86 (ACC)\\
		\hline
		\cite{06612} & Classify & & x & x & HAM10000, BCN-20000, MSK & 0.85 (ACC)\\
		\hline
		\cite{03225} & Classify & & x & & HAM10000 & 0.85 (ACC)\\
		\hline
		\cite{12602} & Classify & & x & & HAM10000 & 0.92 (AUC)\\
		\hline
		\cite{03426} & Classify & & x & & HAM10000 & 0.92 (AUC)\\
		\hline
		\cite{03910} & Classify & & x & & HAM10000 & 0.74 (recall)\\
		\hline
		\cite{05045} & & Classify & x & x & HAM10000 & \\
		\hline
		\cite{2101.133} & Classify&  & x &  & HAM10000 & 0.92 (ACC)\\
		\hline
		\cite{22750} & Seg&  &  &  & HAM10000 & 0.99 (ACC)\\
		\hline
		\cite{9445180} & Seg &  &  &  & HAM10000 & 0.97 (ACC)\\
		\hline
	\end{tabular}
	\caption{Related Works Summary.}
	\label{table:related-work-summary}
\end{table}
\subsubsection{Deep Learning Approach}
In Deep Learning, one of the most cutting-edge technologies that have been used is Soft-Attention as stated in \mbox{\cite{03358}}. Soumyyak et al construct several models formed by the combination of a backbone model including DenseNet201 \mbox{\cite{06993}}, InceptionResNetV2 \mbox{\cite{00567}}, ResNet50 \mbox{\cite{03385} \cite{05027}}, VGG16 \mbox{\cite{1556}} and Soft-Attention layer. Their approach is to add the Soft-Attention layer at the end or the middle of the backbone model. For ResNet50 and VGG16, the Soft-Attention layer is added after the third residual block and CNN block, respectively. DenseNet201 and InceptionResNetV2, otherwise concatenate with the Soft-Attention before a fully-connected layer, and then soft-max layer. Soumyyak et al proposed method gain a greate performance and also outperform many other studies with the accuracy of 0.93 and the precision of 0.92. However using the Data Augmentation on an imbalanced data set make the model cannot classify well on all of the classes, therefore their model got the recall and f1-score of 0.71 and 0.75, respectively. In this research, our proposed method also consider this problem and solve it.

Using those above backbones has been tried by many previous researches. Rishu Garg et al \mbox{\cite{03798}} uses transfer learning approach with CNN based model: ResNet50 and VGG16 which are pretrained with ImageNet data set. Besides, they also use data augmentation to avoid the imbalance of the data set. Histogram Equalization is also used to increase the contrast of the skin lesions before feeding into the Machine Learning algorithms including Random Forest, XGBoost, Support Vector Machine.	Histogram Equalization can be consider as a heat map that takes the main feature as the number of occurrences of the same value pixel. This approach also gain great performance with the accuracy of 0.90 and the precision of 0.88. However this approach can be bias since the one skin image of the data set contain the skin lesion at the center and the background skin so that histogram may treat background with more number of occurrence of the same pixel value. In this research, our proposed method use the Soft-Attention which can create a heat map feature of the lesion. Otherwise, Rishu Garg et al proposed method also face the problem of imbalanced classifying due to the imbalanced data set with the f1-score and recall is 0.77 and 0.74, respectively.

Instead of using the whole imbalanced data set, Abayomi-alli et al decide to separate the data set into two subset, one contains only melanoma and the other one contains the rest \mbox{\cite{2101.133}}. Before feeding the data to classify the melanoma, the training data is then augmented by SMOTE method. SMOTE creates artificial instances by oversampling the minority class. SMOTE recognizes k-minority class neighbors that are near to each minority class sample by using the covariance matrix. This approach got the accuracy, recall and f1-score of 0.92, 0.87 and 0.82, respectively.

@@

Abnormal, skin lesion segmentation, on the other hand, also play an important role in skin lesion classification. Nawaz et al create a framework for Melanoma segmentation \mbox{\cite{22750}}. Their proposed method is Unet model but using the backbone is densenet77 and all residual block is changed into dense block which contains a sequence of Convolution and an Average Pooling. This melanoma segmentation approach got the accuracy of 0.99. Kadry et al, otherwise, using Unet model with VGG deep convolution layer, pooling on the skip connection. This approach can completely extract the whole lesion, though overlap by hair. This approach got the accuracy of 0.97.

@@

\begin{figure}[!htb]
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{Definitions/CM/dn201cm}
		\caption{DenseNet201 Confusion Matrix}\label{fig:densenet201cm}
	\end{minipage}\hfill
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{Definitions/CM/irv2cm}
		\caption{InceptionResNetV2 Confusion Matrix}\label{fig:irv2cm}
	\end{minipage}
\end{figure}

@@

\begin{table}[H]
	\centering
	\begin{tabular}{| l | c  c | }
		\hline
		Model & AUC(AD) & AUC(MD)\\ 
		\hline
		InceptionResNetV2 & 0.971 & \textbf{0.975}\\
		\hline
		DenseNet201 & 0.93 & \textbf{0.97}\\
		\hline
		ResNet50 & \textbf{0.95} & 0.93 \\
		\hline
		ResNet152 & 0.97 & 0.87\\
		\hline
		NasNetLarge & - & \textbf{0.96}\\
		\hline
		MobileNetV2 & 0.95 & \textbf{0.97}\\
		\hline
		MobileNetV3Small & 0.67 & \textbf{0.96}\\
		\hline
		MobileNetV3Large & 0.96 & \textbf{0.97}\\
		\hline
		NasNetMobile & 0.96 & \textbf{0.97}\\
		\hline
	\end{tabular}
	\caption{AUC (area under the curve) of all models. AD stands for augmented data, this indicate that the model is trained with augmented data. MD stands for Metadata which indicate that the model is trained with Metadata}
	\label{table:overall-auc}
\end{table}

\begin{figure}[!htb]
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{Definitions/ROC/densenet201}
		\caption{DenseNet201 Class ROC}\label{fig:densenet201auc}
	\end{minipage}\hfill
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{Definitions/ROC/irv2}
		\caption{InceptionResNetV2 Class ROC}\label{fig:irv2auc}
	\end{minipage}
\end{figure}

@@

\section{Conclusions}
In this research, our proposed is to construct a model as a combination of backbone models and Soft-Attention. Moreover, the model takes two inputs including image data and metadata. besides, a new weight loss function is applied to figure out the data imbalance problem. Finally, the combination of InceptionResNetV2, Soft-Attention, and Metadata is the best model with the accuracy of 0.9. Although the accuracy and the precision of the model are not the highest, the f1-score, recall, and AUC-score of 0.86, 0.81 and 0.975, respectively is the highest and the most balanced indicator. Therefore, InceptionResnetV2 can classify well in all classes including low samples classes. Otherwise, during the experiment, the combination of MobileNetV3, Soft-Attention, and Metadata achieve an accuracy of 0.86 that is nearly the same as InceptionResNetV2, though with fewer number parameters and depth. Therefore the infer time is much less than the InceptionResNetV2. This result opens the door to constructing a great performance model that can be applied to mobile, IoT devices. \add[H.K.D]{As the result, proposed method and others still face the problem of badly distinguish between melanoma and black nevus because in some cases, the melanoma and the nevus image has the same lesion size and color.}
\vspace{6pt}

@@

\dataavailability{The code and the data analysis report can be found here: \\https://github.com/ScaleMind-C9308A/Skin-Disease-Detection-HAM100000.git}

@@

\bibitem[Author2(year)]{2101.133}
OLUSOLA OLUWAKEMI ABAYOMI-ALLI, ROBERTAS DAMAŠEVIČIUS,,
SANJAY MISRA, RYTIS MASKELIŪNAS, ADEBAYO ABAYOMI-ALLI Malignant skin melanoma detection using image augmentation by oversampling in nonlinear lower-dimensional embedding manifold
{\em TUBITAK} 
{\bf 2021}.

\bibitem[Author2(year)]{22750}
Marriam Nawaz, Tahira Nazir, Momina Masood, Farooq Ali, 
Muhammad Attique Khan, Usman Tariq, Naveera Sahar,
Robertas Damaševicius Melanoma segmentation: A framework of improved
DenseNet77 and UNET convolutional neural network
{\em Wiley} 
{\bf 2022}.

\bibitem[Author2(year)]{9445180}
Seifedine Kadry, David Taniar, Robertas Damaševičius, Venkatesan Rajinikanth, Isah A. Lawal,
Robertas Damaševicius Extraction of Abnormal Skin Lesion from
Dermoscopy Image using VGG-SegNet
{\em Wiley} 
{\bf 2022}.
\end{thebibliography}
